Developing a Bubble Chamber Particle Discriminator Using Semi-Supervised Learning

### 2018-11-22 documentation/authors.tex
Added more authors and email

\author[1]{B.~Matusch \thanks{Corresponding: \url{brendon.matusch@snolab.ca}}}
\affil[1]{SNOLAB, Lively, Ontario, P3Y 1N2, Canada}

@@

\author[4]{D.~M.~Asner \thanks{now at Brookhaven National Laboratory}}

@@

\author[2]{U.~Chowdhury \thanks{now at Canadian Nuclear Laboratories}}

@@

@@

@@

@@

\author[5]{J.~Zhang \thanks{Argonne National Laboratory}}

>>>>

\author[1]{B.~Matusch\thanks{Corresponding: \url{brendon.matusch@snolab.ca} or \url{analysis@picoexperiment.com}}}
\affil[1]{SNOLAB, Lively, Ontario, P3Y 1N2, Canada}

@@

\author[4]{D.~M.~Asner\thanks{now at Brookhaven National Laboratory}}

@@

\author[2]{U.~Chowdhury\thanks{now at Canadian Nuclear Laboratories}}

@@

\author[13]{T.~Hillier}

@@

\author[13]{C.~Licciardi}

@@

\author[13]{E.~Weima}

@@

\author[5]{J.~Zhang\thanks{now at Argonne National Laboratory}}
